\documentclass[a4paper,10pt]{article}

% Packages
\usepackage{parskip}
\usepackage{hologo}
\usepackage{fontspec}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue
}
\usepackage{color}
\usepackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9, top=0.4in, bottom=0.4in]{geometry}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{supertabular}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{multirow}
\usepackage[style=authoryear,sorting=ynt,maxbibnames=2]{biblatex}
\usepackage{fontawesome5}
\usepackage[normalem]{ulem}

\setmainfont{Arial}
\color[HTML]{110223}
\addbibresource{citations.bib}

% Customizations
\newcolumntype{C}{>{\centering\arraybackslash}X}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.42\textwidth}
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{1pt}{2pt}{2pt}
\setlength\bibitemsep{1em}

% Document
\begin{document}
\fontsize{10}{12}\selectfont
\pagestyle{empty}

% Name and Contact
\begin{tabularx}{\linewidth}{@{}C@{}}
\Huge{Sujal Bagade} \\[6pt]
\end{tabularx}

\begin{tabularx}{\linewidth}{@{}C@{}C@{}C@{}}
\href{mailto:sujalbagade123@gmail.com}{\raisebox{-0.05\height}{\faEnvelope} sujalbagade123@gmail.com} \hspace{0.2cm}
\raisebox{-0.05\height}{\faMobile} +91 9921872905 \hspace{0.2cm}
\href{https://www.linkedin.com/in/sujalbagade}{\raisebox{-0.05\height}{\faLinkedin} linkedin.com/in/sujalbagade}
\end{tabularx}

% Education
\section{\textbf{Education}}
\begin{tabularx}{\linewidth}{@{}X r@{}}
\textbf{Dr. D Y Patil Institute of Technology} & \textbf{Dec 2021 -- June 2025} \\
BE in Computer Engineering | CGPA: 8.9/10 \\
Honours in Data Science \\
\\
\textbf{Matoshri Junior College} & \textbf{Aug 2019 -- Jul 2021} \\
Higher Secondary Education | Percentage: 89\% \\
\end{tabularx}

% Skills
\section{\textbf{Skills}}
\begin{itemize}[nosep,leftmargin=*]
    \item \textbf{Certifications}: 
    \href{https://www.coursera.org/account/accomplishments/verify/FV8DSDL7DVVZ}{Google Cloud Fundamentals (Google Cloud)}, 
    \href{https://www.coursera.org/account/accomplishments/verify/9S7N4TJ68C98}{Back-End Development (Meta)}, 
    \href{https://credentials.databricks.com/c4992167-4627-41fd-998f-1a64555d43ff#acc.gc3NZh2P}{Databricks Generative AI Fundamentals}.
    \item \textbf{Technical Skills}: C, C++, Java, Python, HTML, CSS, JavaScript, React, Solidity, Docker.
    \item \textbf{Tools}: Google Cloud Console, AWS, Git, GitHub, Postman, Ganache, Truffle, Canva, Figma.
    \item \textbf{Others}: Leadership, Management, Communication, Problem Solving.
\end{itemize}

% Experience
\section{\textbf{Experience}}
\begin{tabularx}{\linewidth}{@{}X r@{}}
\textbf{Software Engineer} -- XDE Studios & \textbf{Jan 2024 -- Present} \\
\end{tabularx}
\begin{itemize}[nosep,leftmargin=*]
    \item Developed and managed ML models, AI solutions, and RAG systems to optimize product functionality.
    \item Led creation of an NFT platform using Blockchain, Solidity, and React.
    \item Built data processing and visualization systems with FastAPI, OpenCV, PaddleOCR, and React.
\end{itemize}

\begin{tabularx}{\linewidth}{@{}X r@{}}
\textbf{Blockchain Lead} -- Google Developer Students Club & \textbf{Oct 2024 -- Present} \\
\end{tabularx}
\begin{itemize}[nosep,leftmargin=*]
    \item Conducted workshops for 100+ students on DApps, smart contracts, and NFTs.
    \item Guided development of DeFi and tokenization projects.
\end{itemize}

\begin{tabularx}{\linewidth}{@{}X r@{}}
\textbf{Secretary} -- Association of Computer Engineering Students & \textbf{June 2023 -- Present} \\
\end{tabularx}
\begin{itemize}[nosep,leftmargin=*]
    \item Advanced the club's mission of promoting technical excellence.
    \item Maintained communication with members and external organizations.
\end{itemize}

% Projects
\section{\textbf{Projects}}
\begin{tabularx}{\linewidth}{@{}X@{}}
\textbf{PORTVISION} \\
\end{tabularx}
\begin{itemize}[nosep,leftmargin=*]
    \item Built a camera control system for shipping ports: snapshot capture, XML camera settings, container monitoring.
    \item Tech stack: FastAPI, OpenCV, PaddleOCR, React, Material UI, HTTP Digest Authentication.
\end{itemize}

\begin{tabularx}{\linewidth}{@{}X@{}}
\textbf{SCALP-SENSE} \\
\end{tabularx}
\begin{itemize}[nosep,leftmargin=*]
    \item Developed a ML model to detect scalp conditions using TensorFlow.
    \item Deployed solution using Python, React, FlaskAPI.
\end{itemize}

\begin{tabularx}{\linewidth}{@{}X@{}}
\textbf{RAGBOT} \\
\end{tabularx}
\begin{itemize}[nosep,leftmargin=*]
    \item Created a chatbot platform with Retrieval-Augmented Generation (RAG) and vectorized storage.
    \item Built with Python, React, FlaskAPI; deployed on AWS EC2.
\end{itemize}

% Achievements
\section{\textbf{Achievements}}
\begin{itemize}[nosep,leftmargin=*]
    \item Winner: All India Blockchain Alliance Hackathon 2023 (\href{https://drive.google.com/file/d/1Z7MJC7KW8R31a5CgrEwE7D2boVf6nebi/view}{Link}).
    \item Completed 120+ Google Cloud Skills Boost Labs (\href{https://www.cloudskillsboost.google/public_profiles/092c7019-a54d-4eb6-9c63-cc42c4bc8909}{Link}).
    \item 9 Google Cloud Badges Earned (\href{https://www.cloudskillsboost.google/public_profiles/092c7019-a54d-4eb6-9c63-cc42c4bc8909}{Link}).
    \item Runner-up: Actual01 Python Hackathon.
    \item Runner-up: DevClash (Web3 Hackathon).
    \item Rank 7 (Internal Hackathon): Smart India Hackathon.
\end{itemize}

\end{document}
